### 2023-06-07 manuscript/chapters/1_intro.qmd
id rather not lose my changes now lmao

## Networks of rate neurons

Networks of rate neurons model the time evolution of the potential $h_i(t) \,[\textrm{V}]$ associated to $N$ individual neurons labeled $i\in\{1,\cdots,N\}$. In their most general form, a connectivity matrix $J_{ij}$ describes the amplitude of the recurrent currents $I^\text{rec}_{ij} = J_{ij} \phi(h_j(t)) \,[\textrm{A}]$ emitted by neuron $j$ and received by neuron $i$. The (monotonically increasing) function $\phi(h)$ has units of $\textrm{Hz}$, and describes the spike firing rate of a given neuron as a function of its potential. In the absence of recurrent currents, the potential of each neuron decays exponentially with time constant $\tau \,[\textrm{s}]$. Neurons can also receive external currents $I^\text{ext}_i(t) \,[\textrm{A}]$. Conversion of current to voltage happens through the resistivity factor $R_i \,[\textrm{Ohm}]$. @eq-rnn writes out the full equation a rate neural network.

$$
\tau \dot h_i(t) = \underbrace{-h_i(t)}_{\text{exponential decay}} + R_i \sum_{j=1}^{N} \underbrace{J_{ij} \phi(h_j(t))}_{I^\text{rec}_i(t)} + R_i I^{\text{ext}}_i(t)
$$ {#eq-rnn}

This model can intuitively be seen as the $N \rightarrow \infty$ limit of a network of spiking neurons, in which neurons emit current spikes (modeled as $\delta$-functions) at some time-variable rate $\phi(h_i(t))$. The convergence is formally proven in @schmutz2023convergence.

In the following, we set $\tau=1$ and $R_i=1$ for all neurons $i$, since these just correspond to rescaling time and currents. Additionally, we consider $I^\text{ext}_i(t)=0$ to simplify the model.

## Convergence to a neural field equation

Neural field equations emerge from the structure of rate neural networks as the number of neurons $N$ becomes large. Positions $\vec \xi_i \in \Rp$ are attributed to each neuron, and define the *embedding space*. If the embedding is well-chosen, then as $N \rightarrow \infty$ neurons close in the embedding space tend to have similar potentials $h_i(t)$, such that these tend to a continuum $h(t, \vec z)$, where $\vec z \in \Rp$.

@@

In the litterature, the embedding space is often thought of as being closely related to the physical positions of the neurons @Bressloff2012. Rigorous proofs of convergence are still an active area of study @chevallier2018mean and are not the subject of this report.

The results we present here should hold for any neural field, but for the sake of argument we shall consider a low-rank rate neural network, for which there are informal proofs of convergence to a neural field equation  @schmutz2023convergence \[TODO : reformulate this\]. Low-rank neural networks hold their name from the rank of their connectivity matrix, defined in @eq-lrj.

$$
J_{ij} = \frac 1N \sum_{\mu=1}^p F_{\mu,i} G_{\mu,j}
$$ {#eq-lrj}

In the case that $\vec F_i = (F_{1,i},\cdots,F_{p,i}) \in \Rp$ sample from some $p$-dimensional distribution $\rho$, the vectors $\vec F_i$ define a "natural embedding" of neuron $i$ in $\Rp$. When the number of neurons increases, the numeric density of neurons in the embedding approaches the actual probability distribution $\rho$, and we can intuitively see the convergence towards a connectivity kernel $w(\vec z, \vec y) = \sum_{\mu=1}^p z_\mu g_\mu(y_\mu)$.

## A one-dimensional neural field

The paper @jabin2022meanfield provides some motivation for the existence of an equivalent neural field in one dimension. Their main result is that under some boundedness assumptions of the connectivity, the limiting equation describing the dynamics of the system incorporates only an integral over $[0,1]$. In our low-rank case, the weights scale as $J_{ij} \sim \frac 1N$, and so we can expect that it should be possible to perform a change of variables from $\Rp$ to $[0,1]$.

The idea is that we define a measurable mapping $S : \Rp \mapsto [0,1]$ and a measure $\mu : [0,1] \mapsto \mathbb{R}^+$ on $([0,1], \mathcal B([0,1]))$, such that we can write the change of variables in the integral :

$$
\int_{\mathbb{R}^p} w(\vec z, \vec y) \phi(h(t, \vec y)) \rho(\mathrm d \vec y) = \int_{[0,1]} [w(\vec z, \cdot) \phi(h(t, \cdot)) \rho(\cdot)] \circ S^{-1} \; \mathrm d \mu
$$

@@

1. A neuron-based simulation of $N$ neurons. Each neuron samples the probability distribution $\rho(z_1, \cdots, z_p)$ independantly. This case then just reduces to simulating the network of rate neurons, which follows @eq-rnn. In other words, we are simulating the full network of rate neurons, and the simulation converges to the true mathematical neural field equation as $N$ becomes large.

@@

In some sense, we would like to find a mapping that conserves "locality" : populations that are close in $\Rp$ should also be close in $[0,1]$, or at least there shouldn't be "too many large discontinuities". @sec-mapping is dedicated to the discussion of these mappings, and gives various numerical demonstrations of the resulting dynamics.

>>>>

## Neural field models in neuroscience

Early recordings of the cat's somatosensory @Mou57 visual cortices suggested that the cortical sheet is organized in vertical columns of functionally similar neurons.

The putative columnar organization of the cortex motivated the design of spatially structured models of neural population dynamics, namely neural field models [@WilCow73;@Nun74;@Ama77], where the spatial dimensions were nothing but the two dimensions of the cortical sheet.

As models of spatiotemporal neural population dynamics on the cortical sheet, neural field models can be used to explain experimentally observed patterns of cortical activity, such as travelling waves in visual [@SatNau12;@MulRey14], somatosensory [@PetHah03;@FerBol06], motor [@RubRob06;@TakKim15], and hippocampal [@LubSia09;@PatFuj12;@PatSch13] cortices (see @MulCha18 for a review), and are used to model large-scale brain signals, such as electroencephalography (EEG) recordings @Bre17. See also @DipRan18 for an example of neural field modelling of 2-photon calcium imaging recording of visual cortex @DipRan18.

More recent recording methods, especially in rodents, have provided evidence of low-dimensional organization of neuronal activity that does not depend on the physical locations of neurons on the cortical sheet. For example, contrary to cat's visual cortex, the orientation selectivity of pyramidal neurons in rat's visual cortex does not depend on their locations, that is, orientation selectivity is heterogeneous at any given location @OhkChu05. Moreover, the activity of interneurons in any small volume of visual cortex is also heterogeneous and seems to be structured by a low-dimensional transcriptomic manifold of fine cell subtypes @BugDuf22. The local functional heterogeneity of neuronal activity in cortex challenges the old concept of functionally homogeneous cortical columns and, with it, classical neural field models.

While, historically, the spatial dimensions in neural field models have been the two dimensions of the cortical sheet (with the notable exception of the ring models for orientation selectivity in visual cortex @BenBar95 and the head-direction system @Zha96), the ``space'' in neural field models does not need to represent physical space but can represent any suitable abstract embedding space. Neural field models with abstract embedding spaces could constitute a generalization of classical neural field theory for cortical networks that are not solely structured by distances of neurons on the cortical sheet.

If we consider neural fields in abstract embedding spaces, which embedding space should we choose? More fundamentally, given some spatio-temporal dynamics, is there a ``natural'' choice for the embedding space?

The goal of this Master Thesis is to show that the answer to the second question is highly nontrivial because even the dimensionality of the embedding space, for some given spatio-temporal dynamics, is not clearly defined if we don't specify the regularity (the ``smoothness'') of the neural fields along the spatial dimensions.

In particular, we show that for any two-dimensional neural field equation (that is, with two spatial dimensions), there is a one-dimensional neural field equation on the interval, where the embedding space is simply the interval $[0,1]$, from which the solution to the two-dimensional equation can be fully reconstructed. The mapping from the two-dimensional equation to the one-dimensional equation is done via well-known measurable bijections for the square $[0,1]^2$ and the interval $[0,1]$. Importantly, these bijections are not (and can't be) diffeomorphisms. Also, we show that despite the fact that the connectivity kernel of the one-dimensional equation is not continuous, it is sufficiently regular for its solution to be numerically approximated using standard mesh-based simulations.

Our result shows that the notion of (spatial) dimensionality in neural field dynamics is not well-defined if not associated with a constraint on the regularity of the neural fields (or the connectivity kernel). Thereby, this work, by studying a simple toy model, illustrates the importance of the analytic notion of regularity when neural population dynamics over abstract continuous spaces are considered.

This work was inspired by recent mathematical development in mean-field theory involving the theory of graphons \cite{JabPoy21}.

## Neural fields as the limit of spatially-structured networks of neurons

<!-- Valentin Schmutz: Which structure? At this point, the reader can't guess that you are talking about spatial structure. For the logic of this section, you should first gently introduce the notion of spatial structure.
Nicole : the papers you give for the introduction should give a good understanding of the spatial structure -->

Neural field equations emerge from the structure of rate neural networks as the number of neurons $N$ becomes large. Positions $\vec z_i \in \Rp$ are attributed to each neuron, and define the *embedding space*. If the embedding is well-chosen, then as $N \rightarrow \infty$ neurons close in the embedding space tend to have similar potentials $h_i(t)$, such that these tend to a continuum $h(t, \vec z)$, where $\vec z \in \Rp$.

@@

In the litterature, the embedding space is often thought of as being closely related to the physical positions of the neurons @Bre11. Rigorous proofs of convergence are still an active area of study @CheDua19 and are not the subject of this report.

## Motivation for a one-dimensional neural field

[TODO : extra motivation, see Valentin's intro]

The paper @JabPoy21 provides some motivation for the existence of an equivalent neural field in one dimension. Their main result is that under some boundedness assumptions of the connectivity, the limiting equation describing the dynamics of the system incorporates only an integral over $[0,1]$. In our low-rank case, the weights scale as $J_{ij} \sim \frac 1N$, and so we can expect that it should be possible to perform a change of variables from $\Rp$ to $[0,1]$.

The idea is that we define a measurable mapping $S : \Rp \mapsto [0,1]$ and a measure $\lambda : [0,1]^2 \mapsto \mathbb{R}^+$, such that we can write the change of variables in the integral :

$$
\int_{\mathbb{R}^p} w(\vec z, \vec y) \phi(h(t, \vec y)) \rho(\mathrm d \vec y) = \int_{[0,1]} [w(\vec z, \cdot) \phi(h(t, \cdot)) \rho(\cdot) \lambda(\cdot)] \circ S^{-1}(\d \alpha)
$$

@@

1. A neuron-based simulation of $N$ neurons. Each neuron samples the probability distribution $\rho(z_1, \cdots, z_p)$ independantly. This case then just reduces to simulating the network of rate neurons. In other words, we are simulating the full network of rate neurons, and the simulation converges to the true mathematical neural field equation as $N$ becomes large.

@@

In some sense, we would like to find a mapping that conserves "locality" : populations that are close in $[0,1]$ should represent nearby populations in $\Rp$, or at least there shouldn't be "too many large discontinuities".

## Summary of contents

@sec-nf introduces a toy model for a neural field in $p$ dimensions, and we discuss interpretations of numerical simulation schemes.

@sec-mappings is dedicated to the discussion of mappings from 2 dimensions to 1 dimension, we give intuitions accompanied by simulations, and discuss in detail how "locality" emerges from these mappings.

Finally, @sec-locality tries to formalize the intuitive results obtained in the previous chapters. We build a metric to measure the "discretization error", and provide the key arguments for a proof of convergence of the numerical approximations.

### 2023-06-07 manuscript/chapters/2_neural_fields.qmd
id rather not lose my changes now lmao

# A simple model for a neural field in 2D

@@

### Case study : low-rank networks of neurons

@@

$$
\begin{aligned}
\dot h_i(t) = -h_i(t) + \frac 1N \sum_{\mu=1}^p \sum_{j=1}^N F_{\mu i} G_{\mu j} \phi(h_j(t)) \\
F_{\mu i} = f_\mu(z_{1 i}, \cdots, z_{p i}),\, G_{\mu i} = g_\mu(z_{1 i}, \cdots, z_{p i}),\, \vec{z_i} \stackrel{\text{iid}}{\sim} \rho
\end{aligned}
$$

@@

@@

$$
\begin{aligned}
f_\mu(z_1, \cdots, z_p) = z_\mu \\
g_\mu(z_1, \cdots, z_p) = \tilde \phi(z_\mu) = \frac{\phi(z_\mu) - \avg{\phi(z_\mu)}}{\mathrm{Var}[\phi(z_\mu)]} \\
\phi(z) = \frac{1}{1+\mathrm{e}^{-z}} \\
\vec{z} = (z_1, \cdots, z_p) \sim \rho(z_1, \cdots, z_p) = \prod_{\mu=1}^p \mathcal{N}(z_\mu),\, \mathcal{N}(z) = \frac{1}{\sqrt{2 \pi}} \mathrm{e}^{-\frac 12 z^2} \\
\end{aligned}
$$

study of fixed points

@@

[TODO FIG : draw a flow field of in the latent space]
[TODO FIG : numerical eigenvalues plot]

@@

![simulation in 2D, p=2](figures/embedding_d=2_h0=0.mp4)

[TODO FIG : scatterplot of the network, with animation]

@@

### Direct simulation of the low-rank neural field

Introduce the neural field in 1D, then 2D

@@

$$
\begin{aligned}
\partial_t h(t, \vec z) &= -h(t, \vec z) + \int_{\mathbb{R}^p} w(\vec z, \vec y) \phi(h(t, \vec y)) \rho(\mathrm d \vec y),
\quad
w(\vec z, \vec y) = \sum_{\mu=1}^p \tilde \phi (y_\mu) z_\mu
\end{aligned}
$$

@@

simulation strategies : grid and sampling

[TODO : show the connectivity with grid sampling. mention that the problems with the compact support get adressed later in the next chapter, when we do $\R^2 \mapsto [0,1]^2$]

## Characterizing dynamics

@@

[TODO : i'm not even sure that introducing the overlaps in necessary. we might just include them for completeness, and because they are relevant in papers on low-rank stuff]

@@

@@

with these definition, we have in our case
$$
\begin{aligned}
\dot \kappa_\mu(t) &= -\kappa_\mu(t) + \int_{\Rp} \tilde\phi(y_\mu) \phi(h(t, \vec y)) \rho(\mathrm d \vec y) = -\kappa_\mu(t) + m_\mu(t) \\
\kappa_\mu(0) &= \int_{\mathbb{R}^p} y_\mu h(0, \vec y) \rho(\mathrm d \vec y)
\end{aligned}
$$

@@

[TODO MATH : actually we could also juste compute the kappa as a function of time, and study that]

### Dynamics in the overlap latent space

Relation between $p$-dimensional closed system and neural field equation in $\mathbb R^p$

$$
\begin{aligned}
\partial_t h(t, \vec z) &= \partial_t h^\perp(t, \vec z) + \sum_{\mu=1}^p z_\mu \dot \kappa_\mu(t) \\
&= -h^\perp(t, \vec z) - \sum_{\mu=1}^p z_\mu \kappa_\mu(t) + \sum_{\mu=1}^p z_\mu m_\mu(t) \\
&= -h(t, \vec z) + \sum_{\mu=1}^p z_\mu m_\mu(t)
\end{aligned}
$$

@@

@@

@@

@@

then one can repeat this for the next cycles. basically each cycle is applying an exponential convolution filter

[TODO MATH : the derivation of this, we have an exponential convolution filter]

![](figures/kappa_cycling_p=2.tmp.png)

simulate cycling in p=2

[TODO : might be good to show a simulation where we explicitly simulate $\kappa$ ? but the goal here is just to "prove" the cycling behavior]

## From $\R^2$ to $[0,1]^2$

@@

![](figures/sampling_R2_01.png)

[TODO : does this deserve its own section ? maybe mention it later, we can give a picture of the "isolines" of the 2D gaussian CDF]

## Numerical simulation of neural fields

### Direct sampling

@@

### Bin averaging samples

![](figures/sampling_R2_nogrid_kernel.png)

### Grid over $[0,1]^2$

@@

Doing this is equivalent to the formulation of the binned connectivity matrix.

![](figures/sampling_R2_01_kernel.png)

>>>>

# Neural field toy model and simulations {#sec-nf}

@@

### Low-rank network of neurons

The results we present in this thesis should hold for any neural field, but for the sake of argument we shall consider a low-rank rate neural network, for which there are informal proofs of convergence to a neural field equation  @schmutz2023convergence \[TODO : reformulate this\]. Low-rank neural networks hold their name from the rank of their connectivity matrix, defined in @eq-lrj.

$$
J_{ij} = \frac 1N \sum_{\mu=1}^p F_{\mu,i} G_{\mu,j}
$$ {#eq-lrj}

In the case that $\vec F_i = (F_{1,i},\cdots,F_{p,i}) \in \Rp$ sample from some $p$-dimensional distribution $\rho$, the vectors $\vec F_i$ define a "natural embedding" of neuron $i$ in $\Rp$. When the number of neurons increases, the numeric density of neurons in the embedding approaches the actual probability distribution $\rho$, and we can intuitively see the convergence towards a connectivity kernel $w(\vec z, \vec y) = \sum_{\mu=1}^p z_\mu g_\mu(y_\mu)$.

@@

$$
\begin{aligned}
\dot h_i(t) =& -h_i(t) + \frac 1N \sum_{\mu=1}^p \sum_{j=1}^N F_{\mu i} G_{\mu j} \phi(h_j(t)) \\
F_{\mu i} =& f_\mu(z_{1 i}, \cdots, z_{p i}), \\
G_{\mu i} =& g_\mu(z_{1 i}, \cdots, z_{p i}), \\
&\vec{z_i} \stackrel{\text{i.i.d.}}{\sim} \rho
\end{aligned}
$$

@@

### Gaussian $\mathcal{N}(\vec 0, \mathbb{1}_N)$ low-rank network of neurons

#### Description

@@

$$
\begin{aligned}
f_\mu(z_1, \cdots, z_p) &= z_\mu \\
g_\mu(z_1, \cdots, z_p) &= \tilde \phi(z_\mu) = \frac{\phi(z_\mu) - \avg{\phi(z_\mu)}}{\mathrm{Var}[\phi(z_\mu)]} \\
\phi(z) &= \frac{1}{1+\mathrm{e}^{-z}} \\
\vec{z} &= (z_1, \cdots, z_p) \sim \rho(z_1, \cdots, z_p) = \prod_{\mu=1}^p \mathcal{N}(z_\mu),\\
&\text{where}\ \mathcal{N}(z) = \frac{1}{\sqrt{2 \pi}} \mathrm{e}^{-\frac 12 z^2}
\end{aligned}
$$

#### Study of fixed points and their stability

@@

![spectrum of $K$ for $N=64$](figures/spectrum_N=64.png)

@@

![simulation in 2D, p=2. TODO redo this one with only scatter and latent-](figures/embedding_d=2_h0=0.mp4)

@@

introduce the neural field as a "smooth fitting of the scatterplot"

eq of neural field

### Simulations of the low-rank neural field

we use the RK4 integration scheme, and the integral is decoupled into product of 1D integrals, each is estimated using a dot product

#### Sampling method (Monte-Carlo integration)

@@

$$
\begin{aligned}
\partial_t h(t, \vec z) &= -h(t, \vec z) + \int_{\Rp} w(\vec z, \vec y) \phi(h(t, \vec y)) \rho(\mathrm d \vec y),
\quad
w(\vec z, \vec y) = \sum_{\mu=1}^p \tilde \phi (y_\mu) z_\mu
\end{aligned}
$$

@@

simulation : when we simulate a network of neurons with $N \gg 1$, we are approximating the integral using a monte carlo method.

Monte-carlo estimation of the integral is

$$
\begin{aligned}
\mathcal{I}(\vec z) &= \int_{\Rp} \underbrace{w(\vec z, \vec y) \phi(h(t, \vec y))}_{I(\vec z, \vec y)} \rho(\d \vec y) \\
\hat{\mathcal{I}}(\vec z) &= \frac 1N \sum_{i=1}^N I(\vec z, \vec{y_i}), \, \vec{y_i} \stackrel{\text{i.i.d.}}{\sim} \rho
\end{aligned}
$$

Numerically, we are estimating $\hat{\mathcal{I}}(\vec z)$, and we can show the convergence rate is in $\bO(1/\sqrt{N})$, since

$$
\begin{aligned}
\mathrm{Var}\left[\hat{\mathcal{I}}(\vec z) \right] &= \frac 1N \mathrm{Var}_{\vec y \sim \rho}[I(\vec z, \vec y)]
\end{aligned}
$$

Detail : strictly speaking, MC samples new points every timestep, here we sample once at t=0, then propagate these points

#### Grid method (Trapezoidal integration)

This method describes the trapezoidal method of integration. We state the result that the convergence rate is $\bO(N^{-2/p})$. For $p \geq 4$, MC shows better scaling behavior (but prefactors of error can change which method is better).

In our case, since the distribution $\rho$ can be factorized, we can decouple the $p$-dimensional integral into the product of $p$ one-dimensional integrals. Then the error estimation of the integral scales as $\bO(N^{-2})$. For this reason, we use the grid method for the remainder of this thesis.

## Characterizing dynamics of the low-rank neural field

@@

[TODO : i'm not even sure that introducing the overlaps in necessary. we might just include them for completeness, and because they are relevant in papers on low-rank stuff. in the rest, just use the kappa for the latent space]

[TODO : do not expand mathematically, say this is well-known and given for context. the fixed point and stability study is new though]

@@

cite @veltz2009localglobal for this.

on explicite les equations du paper dans notre cas

introduce this a just the projection of the field on the fixed points

@@

with these definitions, we have in our case
$$
\begin{aligned}
\dot \kappa_\mu(t) &= -\kappa_\mu(t) + \int_{\Rp} \tilde\phi(y_\mu) \phi(h(t, \vec y)) \rho(\mathrm d \vec y) = -\kappa_\mu(t) + m_\mu(t) \\
\kappa_\mu(0) &= \int_{\mathbb{R}^p} y_\mu h(0, \vec y) \rho(\mathrm d \vec y)
\end{aligned}
$$

and the orthogonal component evolves according to

$$
h^\perp(t, \vec z) = h^\perp(0, \vec z) \mathrm e^{-t},
\quad
h^\perp(0, \vec z) = h(0, \vec z) - \sum_{\mu=1}^p \kappa_\mu(0) z_\mu
$$

todo : put accent on the fact the RHS can be computed using all the kappas, kappa -> h -> integral = m -> RHS

conceptually : do not forget that the kappa is only relevant in this particular toy model, in general we do not have these kappa, and the study of low-dim fields is interesting. If we always had the kappa, then of course we can only look at the kappa, since much simpler (a 1D manifold (line) in a Rp space, instead of a Rp volume in a Rp space).

<!-- Relation between $p$-dimensional closed system and neural field equation in $\mathbb R^p$
$$
\begin{aligned}
\partial_t h(t, \vec z) &= \partial_t h^\perp(t, \vec z) + \sum_{\mu=1}^p z_\mu \dot \kappa_\mu(t) \\
&= -h^\perp(t, \vec z) - \sum_{\mu=1}^p z_\mu \kappa_\mu(t) + \sum_{\mu=1}^p z_\mu m_\mu(t) \\
&= -h(t, \vec z) + \sum_{\mu=1}^p z_\mu m_\mu(t)
\end{aligned}
$$ -->

@@

@@

<!-- [TODO FIG : draw a flow field of in the latent space. -> actually, might be difficult when there is delay] -->

@@

### Intuition behind the cycling

@@

### Cycling behavior of the latent variables

@@

then one can repeat this for the next cycles. basically each cycle is applying an exponential convolution filter [TODO : trim this, don't go into detail]

<!-- [TODO MATH : the derivation of this, we have an exponential convolution filter] -->

![simulate cycling in p=2](figures/kappa_cycling_p=2.tmp.png)

## Mapping $\R^2$ to $[0,1]^2$ using the CDF

<!-- ### Using the CDF -->

later we will map [0,1]² -> [0,1], so we first want to map R² -> [0,1]².

there are many ways to do this using functions R -> [0,1], but a practical choice is the inverse CDF, which has the added benefit of absorbing the density in the kernel, in the sense that the integral over [0,1]² becomes "weighted" by a uniform distribution (lesbesgue measure $\lambda$)

@@

![samples in $\Rp$ and corresponding samples in $[0,1]$](figures/sampling_R2_01.png)

give a picture of the "isolines" of the 2D gaussian CDF

furthermore numerically, mapping R² -> [0,1]² adresses the problem of "putting a finite grid on the infinite R²". (previously we would have had to make the approximation of compact support, then sample the PDF on the grid and numerically renormalize.)

<!-- ### Consequences on simulations

#### Direct sampling

@@

#### Grid over $[0,1]^2$

@@

Doing this is equivalent, but more memory-efficient to the formulation of the binned connectivity matrix.

![](figures/sampling_R2_01_kernel.png) -->
